Religion and Its Influence on Social Issues^[Code and data are available at: https://github.com/dudqo/religion_survey]

### 2022-04-28 outputs/paper/paper.Rmd
format rmd

```{r fig2, fig.cap= "Distribution of survey respondents' race.", echo = FALSE}
reduced_data %>%
  ggplot(aes(x = race, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Race",
       ) +
  theme(legend.position = "none")
```

```{r fig3, echo = FALSE, fig.cap= "Distribution of survey respondents' gender"}
reduced_data %>%
  ggplot(aes(x = gender, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Gender and Opinion on Importance of Being Born as Male or Female",
       ) +
  theme(legend.title = element_blank()) +
  coord_flip() +
  facet_wrap(~opsex)
```
```{r fig4, echo=FALSE, fig.cap = "Distribution of survey respondents' birth place"}
reduced_data %>%
  ggplot(aes(x = relig, fill = born)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Number of Survey Respondents' Born in U.S",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

@@

```{r fig6, echo=FALSE, fig.cap = "Opinion on governmemt policy on improving coditions of black population"}
reduced_data %>%
  drop_na(nation_race) %>%
  ggplot(aes(x = relig, fill = nation_race)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Opinion on goverment spending to improve coditions of Black People",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig7, echo=FALSE, fig.cap = "Opinion on whether the government is spedning on welfare"}
reduced_data %>%
  drop_na(nation_welfare) %>%
  ggplot(aes(x = relig, fill = nation_welfare)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough on Welfare?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig8, echo=FALSE, fig.cap = "Opinion on whether the government is spending enough to assist the poor"}
reduced_data %>%
  drop_na(Assistance_to_the_poor) %>%
  ggplot(aes(x = relig, fill = Assistance_to_the_poor)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig9, echo=FALSE, fig.cap = "Opinion on whether the government is spending enough on social security"}
reduced_data %>%
  drop_na(social_security) %>%
  ggplot(aes(x = relig, fill = social_security)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough on Social Security?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig10, echo=FALSE, fig.cap = "Opinion on whether the government is spending enough to halt increasing crime rate"}
reduced_data %>%
  drop_na(natcrime) %>%
  ggplot(aes(x = relig, fill = natcrime)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Halt Increasing Crime Rate?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig11, echo=FALSE, fig.cap = "Opinion on whether religion should have less influence"}
reduced_data %>%
  drop_na(religinf) %>%
  ggplot(aes(x = relig, fill = religinf)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Would the U.S be a better country if religion had less influence?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig12, echo=FALSE, fig.cap = "Opinion on whether they support same sex marriage"}
reduced_data %>%
  drop_na(homo_marriage) %>%
  ggplot(aes(x = relig, fill = homo_marriage)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Do You Agree With Same Sex Marriage?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig13, echo=FALSE, fig.cap = "Opinion on whether they support abortion"}
reduced_data %>%
  drop_na(abortion) %>%
  ggplot(aes(x = relig, fill = abortion)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Do you agree with abortion for any reason?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

>>>>

```{r fig2, fig.cap= "Distribution of survey respondents race.", echo = FALSE}
reduced_data %>%
  ggplot(aes(x = race, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Race",
       ) +
  theme(legend.position = "none")
```

```{r fig3, fig.cap= "Distribution of survey respondents gender.", echo = FALSE}
reduced_data %>%
  ggplot(aes(x = gender, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Gender and Opinion on Importance of Being Born as Male or Female",
       ) +
  theme(legend.title = element_blank()) +
  coord_flip() +
  facet_wrap(~opsex)
```

```{r fig4, echo=FALSE, fig.cap = "Distribution of survey respondents birth place"}
reduced_data %>%
  ggplot(aes(x = relig, fill = born)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Number of Survey Respondents' Born in U.S",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

@@

```{r fig6, echo=FALSE, fig.cap = "Opinion on governmemt policy on improving coditions of black population"}
reduced_data %>%
  drop_na(nation_race) %>%
  ggplot(aes(x = relig, fill = nation_race)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Opinion on goverment spending to improve coditions of Black People",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig7, echo=FALSE, fig.cap = "Opinion on whether the government is spedning on welfare"}
reduced_data %>%
  drop_na(nation_welfare) %>%
  ggplot(aes(x = relig, fill = nation_welfare)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough on Welfare?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig8, echo=FALSE, fig.cap = "Opinion on whether the government is spending enough to assist the poor"}
reduced_data %>%
  drop_na(Assistance_to_the_poor) %>%
  ggplot(aes(x = relig, fill = Assistance_to_the_poor)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig9, echo=FALSE, fig.cap = "Opinion on whether the government is spending enough on social security"}
reduced_data %>%
  drop_na(social_security) %>%
  ggplot(aes(x = relig, fill = social_security)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough on Social Security?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig10, echo=FALSE, fig.cap = "Opinion on whether the government is spending enough to halt increasing crime rate"}
reduced_data %>%
  drop_na(natcrime) %>%
  ggplot(aes(x = relig, fill = natcrime)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Halt Increasing Crime Rate?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig11, echo=FALSE, fig.cap = "Opinion on whether religion should have less influence"}
reduced_data %>%
  drop_na(religinf) %>%
  ggplot(aes(x = relig, fill = religinf)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Would the U.S be a better country if religion had less influence?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig12, echo=FALSE, fig.cap = "Opinion on whether they support same sex marriage"}
reduced_data %>%
  drop_na(homo_marriage) %>%
  ggplot(aes(x = relig, fill = homo_marriage)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Do You Agree With Same Sex Marriage?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig13, echo=FALSE, fig.cap = "Opinion on whether they support abortion"}
reduced_data %>%
  drop_na(abortion) %>%
  ggplot(aes(x = relig, fill = abortion)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Do you agree with abortion for any reason?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
